Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-02 02_Paper/paper.tex
robot arm plot.

%% The `ecrc' package must be called to make the CRC functionality available
\usepackage{ecrc}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}

@@

\AP{
Predictive analytics as concepts. Implementation in production
\begin{itemize}
       \item Predictive Maintenance
       \item Scheduling
       \item Other
\end{itemize}       
If happens to be something with P.A. Quality Check
\begin{itemize}
       \item	Predictive analytics in production focusing in QA
       \item	Existing approaches and methods
\end{itemize}      
Note: Ideal is to find a gap in literature, that proves why do we do it and why it is important
}

\section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page \OneAim doc bases

@@

\subsection{Classifier optimization and testing}
We work with a total of 132 measurements. Each containing arm and belt data
logs of individual cell runs. 20 samples are set aside at random for testing 
purposes, leaving 112 training samples. The random seed is set to 1

We compare a total of three different classifier architectures on the data.
A Support Vector Machine (SVM), a multilinear perceptron and a Random Forest
structure. 
\begin{table}
       \begin{tabular}{ c c }
              Support Vector Machine & 95.\% \\
              Multilinear Perceptron & 95.\% \\
              Random Forest          & 100\%
       \end{tabular}
       \caption{Method comparison for fault detection using the industry demo data test set.}
       \label{tab:class_comp}
\end{table}
Results are shown in table~\ref{tab:class_comp}. For 55 of the total 132 samples
quality measurements indicate a problem. This sets the 
baseline over the entire data set, that would be obtained by simply labeling all samples
as good. Over the entire data set, we require to classify more than 58.3\% of the data correctly.
The test set contains eight incorrect samples. We would therefore expect the naive classifier
to produce a 60\% accuracy, which we have to beat. In Table~\ref{tab:class_comp},
we observe that this is indeed the case for all three approaches evaluated here.

>>>>

%% The `ecrc' package must be called to make the CRC functionality available
\usepackage{ecrc}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage[mode=buildnew]{standalone}% requires -shell-escape
\usepackage{tikz}
\usepackage{pgfplots}
\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{dateplot}
\pgfplotsset{compat=newest}

@@

\AP{
Predictive analytics as concepts. Implementation in production
\begin{itemize}
       \item Predictive Maintenance
       \item Scheduling
       \item Other
\end{itemize}       
If happens to be something with P.A. Quality Check
\begin{itemize}
       \item	Predictive analytics in production focusing in QA
       \item	Existing approaches and methods
\end{itemize}      
Note: Ideal is to find a gap in the literature, that proves why do we do it and why it is important
}

\section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page \OneAim doc bases
\begin{figure}
       \includestandalone[width=.45\textwidth]{img/cell_data_plot}
       \caption{Robot arm movement patterns.}
\end{figure}

@@

\subsection{Classifier optimization and testing}
We work with a total of 132 measurements. Each containing arm and belt data
logs of individual cell runs. 20 samples are set aside at random for testing 
purposes, leaving 112 training samples. The random number generator seed is
set to one in order to ensure the train and test set splits are identical 
for all experiments.

We compare a total of three different classifier architectures on the data.
A Support Vector Machine (SVM), a multilinear perceptron and a Random Forest
structure. All three methods are trained using standard hyperparameters.
\footnote{In order to allow exact reproduction of these results source
code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
\begin{table}
       \centering
       \begin{tabular}{ c c }
              Support Vector Machine & 95.\% \\
              Multilinear Perceptron & 95.\% \\
              Random Forest          & 100.\%
       \end{tabular}
       \caption{Method comparison for our annomaly detection task 
                using the industry demo data test set.}
       \label{tab:class_comp}
\end{table}
Results are shown in table~\ref{tab:class_comp}. For 55 of the total 132 samples
quality measurements indicate a problem. This sets the 
baseline over the entire data set, that would be obtained by simply labeling all samples
as good. Over the entire data set, we require to classify more than 58.3\% of the data correctly.
The test set contains eight incorrect samples. We would therefore expect any naive classifier
to produce a 60\% accuracy, which we have to beat. In Table~\ref{tab:class_comp},
we observe that this is indeed the case for all three approaches evaluated here.
The random forest performed best in this case.
